\section{Maze-Khepera plant (module)}
\label{sec:mkp}

\subsection{Introduction}
\label{sec:mkp:intro}

We want to find the optimal paths through a maze and pilot the Khepera 
from its position to the target. To do so, the plant needs the maze 
information through the Tapir detector. The action chosen by the 
controller will be send to the DirectedKhepera that will navigate the 
robot
to the target point with the help of an orientation detector 
(Histogram detector or color detector with triangle tracker).

\subsection{Gather information}
\label{sec:mkp:gather}

It first loads the maze with the help of MazeKheperaData. I don't know 
why, but if the detector run once, then the information will still 
be accessible via shared memory even If the detector is down. 
\\
\\
If the parameter with\_robot is set to true, it will construct and 
initialize the robot. Otherwise, it will run as a classic MazePlant 
without Khepera.
If the parameter test\_robot\_block is set to true, the program enters an 
infinite loop and the user is asked to enter $x$, $y$ position 
corresponding 
to the grid positions. This can be used to debug maze block positions. 
This option might be useless now that the plant is working properly.

\subsection{Pilot the Khepera}
\label{sec:mkp:pilot}

The action is chosen by the controller (as in MazePlant) and 
is represented by the next position ($x_g$, $y_g$) in the grid. 
The position is translated by MazeKheperaData to an ($x_i$, $y_i$) position 
in the image which correspond to the center of the grid block. This 
position ($x_i$, $y_i$) is send to DirectedKhepera that navigates the 
Khepera to this position.

\subsection{Improvements}
\label{sec:mkp:improvements}

The most annoying thing with this plant is when we need to abort 
the experiment while the robot is moving. We always need to keep a 
second clsquare running with the option manipulate\_robot=true to be 
able to send a stop command. It would be nice if the plant could catch 
an abort and send automatically a stop command to the Khepera.

\subsection{How to use}
\label{sec:mkp:howto}
    \begin{enumerate}
        \item Set the maze detector. Be sure that the detection is correct.
        \item Start frameview if it is not already running.
        \item ./CLSquare your\_config\_file.cls
        \item If with\_robot=true, stop the maze detector when asked 
            for and start the Khepera detector.
    \end{enumerate}

\subsubsection{Parameters for configuration file}
\label{sec:mkp:params}
    \begin{description} \itemindent=-15pt
        \item[with\_robot] Use the Khepera robot during the experiment 
            (default false)
        \item[manipulate\_robot] Manipulate the Khepera with manual 
            commands (D,l0,l0)
        \item[test\_robot\_blocks] Send manually the Khepera to grid 
            positions ($x_g$, $y_g$)
    \end{description}

The manipulate\_robot and test\_robot\_blocks parameters prevent 
experiments. \clsquare{} stay locked in the init function and quit when 
the infinite loop of manipulate\_robot or test\_robot\_blocks is broken. 
