\section{Multiple object shared memory (class)}
\label{sec:mosmc}

\subsection{Introduction}
\label{sec:mosmc:intro}

The Tapir detector sends multiple objects for the maze detection. I 
needed to built a TapirDetector class to receive those objects from 
shared memory.

The saved objects will be read at the memory address given by the 
pathname and the keyid.

\subsection{Connecting and reading shared memory segment}
\label{sec:mosmc:algo}
Here is the algorithm described in chronological order.

    \begin{enumerate}
        \item It «connects» to a shared memory segment with shmget.
        \item It assigns an index of the shared memory segment for the list 
            of mutexes. (see section \ref{sec:mosmc:ms})
        \item It assigns an index of the shared memory segment for the list 
            of objects. (see section \ref{sec:mosmc:ms})
        \item During update (read value in memory), for each object\_i in objects:
        \begin{enumerate}
           \item It locks the $\mbox{mutex}_i$ of the $\mbox{object}_i$.
            \item Reads the $\mbox{object}_i$.
            \item Releases the $\mbox{mutex}_i$.
        \end{enumerate}
 
    \end{enumerate}

\subsection{Memory structure}
\label{sec:mosmc:ms}
For more information, see section \ref{sec:mosm:ms}

\begin{displaymath}
    n = \mbox{number of objects}
\end{displaymath}
\begin{center}
\begin{tabular}{c|c|c}
\label{tab:mosmc:ms}
   {\bf Rows }      & {\bf Items }  & {\bf Attributes} \\ \hline
   0                & $\mbox{mutex}_1$  & mutex \\ \hline
   $\vdots$         & $\vdots$          & $\vdots$      \\ \hline  
   $n$              & $\mbox{mutex}_n$  & mutex \\ \hline
   $n+1$            & $\mbox{object}_1$ & x \\ \hline
   $n+2$            & $\mbox{object}_1$ & y \\ \hline
   $n+3$            & $\mbox{object}_1$ & size \\ \hline 
   $n+4$            & $\mbox{object}_1$ & angle \\ \hline
   $n+5$            & $\mbox{object}_1$ & runtime \\ \hline
   $\vdots$         & $\vdots$ & $\vdots$ \\ \hline
   $n + (n-1)*5 +1 = (n-1)*6+2 $ & $\mbox{object}_n$ & x \\ \hline
   $n + (n-1)*5 +2 = (n-1)*6+3$ & $\mbox{object}_n$ & y \\ \hline
   $n + (n-1)*5 +3 = (n-1)*6+4$ & $\mbox{object}_n$ & size \\ \hline 
   $n + (n-1)*5 +4 = (n-1)*6+5$ & $\mbox{object}_n$ & angle \\ \hline
   $n + (n-1)*5 +5 = 6*n$ & $\mbox{object}_n$ & runtime
\end{tabular}
\end{center}

\subsection{How to use}
\label{sec:mosmc:howto}

Set the number of objects, key\_path and key\_id as set in the 
configuration file in tapir.

\subsubsection{Parameters config file}
\label{sec:mosmc:howto:params}

    \begin{description} \itemindent=-15pt
        \item[key\_path] pathname for the key of shared memory segment 
                (read about ftok())
        \item[key\_id] key for the shared memory segment (read about ftok())
        \item[nb\_objects] the number of objects to be send
    \end{description}
